Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2017-02-05 MHCpaper/MHCsupp.tex
ko name
typos

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage[inactive,tightpage]{preview}
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
%\newcounter{tablerow}[table]
%\newcommand{\tablerowautorefname}{row}
%\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figurename}{Appendix-figure}
\renewcommand{\figureautorefname}{Appendix-figure}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 #2}}
\captionsetup{labelformat=supp}
\renewenvironment{myenumA}{\begin{inparaenum}[\bfseries A]}{\end{inparaenum}}
% ---------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{K$^\mathrm{b}$D$^\mathrm{b}$-/-}}}
\newcommand{\KO}{K$^\mathrm{b}$D$^{\mathrm{b}-/-}$}
%\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
%\newcommand{\lmax}{_{\text{max}}}
%\newcommand{\lmin}{_{\text{min}}}
\newcommand{\modelfig}[1][A]{Figure 4#1 of the main text}
\newcommand{\datafig}[1][B]{Figure 3#1 of the main text}
\newcommand{\chrfig}[1][B]{Figure 2#1 of the main text}
\newcommand{\compfig}[1][A]{Figure 2 -- figure supplement 2#1}
\newcommand{\basefig}{Figure 1 -- figure supplement 2}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\author{}
\date{}

@@

    \cline{1-9}
    Serial   & 10 & $0.12$  & $0.14$  & $0.2$  & 0.5 & 0.89 & 0.11  & 100  \\%&\label{tr:serial_fit} \\
    Two-state     & 2  & $0.1$  & $0.1$  & $0.2$  & 0.5 & 0.6 & 0.4  & 5   \\%&\label{tr:binary} \\
    Multistate    & 10 & $0.3$  & $0.3$  & $0.4$  & 0.5 & 0.8 & 0.2  & 5   \\%&\label{tr:multistate_lin} \\
    Pooled res.\ & 7  & $0.008$        & $[0.0006,0.6]$  & $[0.001,1]$
                                          & 0.5 & 0.9 & 0.1 & 20 \\%&\label{tr:pooled_deponly}\\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.522 & 0.63 & 0.002  & 200  \\%&\label{tr:cascade_fit} \\
    Non-uni.\ & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 500  \\%&\label{tr:nonuni_fit} \\
    \cline{1-9}
  \end{tabular}}
  \end{myenumA}
\end{preview}
  \caption[Simulation results for various models]{(\ref{fig:serial_sim}-\ref{fig:nonuni_sim}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (solid) and after gain-decrease pre-training (dashed) for wild-type (black) and \KO\ (red) models.
  (\ref{tab:params}) Parameters used for simulations.
  For the serial, two state and multistate models, the plasticity parameter listed is the transition probability between adjacent states.
  For the pooled resource model, the plasticity parameters are the minimum and maximum transition probability for the constituent two-state synapses.
  For the cascade and non-uniform multistate models, the plasticity parameter is the ratio of adjacent transition probabilities.}\label{fig:sim_results}
\end{figure}

@@

\begin{figure}
\begin{preview}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=0.4\linewidth]{pooled_deponly_scan.eps}
\end{preview}
  \caption{Difference in initial learning rate in wild-type models, without and with gain-decrease pre-training.
  Learning, $L(t)$ is defined in \eqref{eq:learning}.
  Here, we show the maximum and minimum values of this quantity when scanning all 6 relevant parameters (see \protect\hyperlink{par:pooled_scan}{text}).
  We see that this quantity is always negative, whereas it was positive in the experiments.
  }\label{fig:pooled_scan}
\end{figure}

@@

    \cline{1-8}
    Serial       & 10 & $0.12$  & $0.14$        & 0.5   & 0.89 & 0.9879 & 100 \\
    Two-state    & 2  & $0.1$   & $0.4$         & 0.5   & 0.7  & 0.91   & 5   \\
    Multistate   & 10 & $0.3$   & $0.3$         & 0.5   & 0.8  & 0.96   & 5   \\
    Pooled res.\ & 7  & $0.08$  & $[0.006,0.6]$ & 0.5   & 0.9  & 0.99   & 20  \\
    Cascade      & 14 & $0.386$ & $0.398$       & 0.522 & 0.63 & 0.99   & 200  \\
    Non-uni.\    & 12 & $0.4$   & $0.4$         & 0.5   & 0.7  & 0.99   & 500  \\
    \cline{1-8}
  \end{tabular}}
  \end{myenumA}
\end{preview}
  \caption[Simulation results for various models]{(\ref{fig:serial_ChR2}-\ref{fig:nonuni_ChR2}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (black) and after non-specific CF stimulation (cyan) for wild-type models.
  (\ref{tab:params_ChR2}) Parameters used for simulations.
  For the serial, two state and multistate models, the plasticity parameter listed is the transition probability between adjacent states.
  For the pooled resource model, the plasticity parameters are the minimum and maximum transition probability for the constituent two-state synapses.
  For the cascade and non-uniform multistate models, the plasticity parameter is the ratio of adjacent transition probabilities.}\label{fig:sim_ChR2}
\end{figure}

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage[inactive,tightpage]{preview}
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
%\newcounter{tablerow}[table]
%\newcommand{\tablerowautorefname}{row}
%\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figurename}{Appendix-figure}
\renewcommand{\figureautorefname}{Appendix-figure}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 #2}}
\captionsetup{labelformat=supp}
\renewenvironment{myenumA}{\begin{inparaenum}[\bfseries A]}{\end{inparaenum}}
% ---------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{\KO}}}
\newcommand{\KO}{DKO}
%\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
%\newcommand{\lmax}{_{\text{max}}}
%\newcommand{\lmin}{_{\text{min}}}
\newcommand{\modelfig}[1][A]{Figure 4#1 of the main text}
\newcommand{\datafig}[1][B]{Figure 3#1 of the main text}
\newcommand{\chrfig}[1][B]{Figure 2#1 of the main text}
\newcommand{\compfig}[1][A]{Figure 2 -- figure supplement 2#1}
\newcommand{\basefig}{Figure 1 -- figure supplement 2}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\author{}
\date{}

@@

    \cline{1-9}
    Serial   & 10 & $0.12$  & $0.14$  & $0.2$  & 0.5 & 0.89 & 0.11  & 100  \\%&\label{tr:serial_fit} \\
    Two-state     & 2  & $0.1$  & $0.1$  & $0.2$  & 0.5 & 0.6 & 0.4  & 5   \\%&\label{tr:binary} \\
    Multistate    & 10 & $0.3$  & $0.3$  & $0.4$  & 0.5 & 0.8 & 0.2  & 5   \\%&\label{tr:multistate_lin} \\
    Pooled res.\ & 7  & $0.008$        & $[0.0006,0.6]$  & $[0.001,1]$
                                          & 0.5 & 0.9 & 0.1 & 20 \\%&\label{tr:pooled_deponly}\\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.478 & 0.63 & 0.002  & 200  \\%&\label{tr:cascade_fit} \\
    Non-uni.\ & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 500  \\%&\label{tr:nonuni_fit} \\
    \cline{1-9}
  \end{tabular}}
  \end{myenumA}
\end{preview}
  \caption[Simulation results for various models]{(\ref{fig:serial_sim}-\ref{fig:nonuni_sim}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (solid) and after gain-decrease pre-training (dashed) for wild-type (black) and \KO\ (red) models.
  (\ref{tab:params}) Parameters used for simulations.
  For the serial, two state and multistate models, the plasticity parameter listed is the transition probability between adjacent states.
  For the pooled resource model, the plasticity parameters are the minimum and maximum transition probability for the constituent two-state synapses.
  For the cascade and non-uniform multistate models, the plasticity parameter is the ratio of adjacent transition probabilities.}\label{fig:sim_results}
\end{figure}

@@

\begin{figure}
\begin{preview}
  \begin{center}
  % Requires \usepackage{graphicx}
  \includegraphics[width=0.4\linewidth]{pooled_deponly_scan.eps}
  \end{center}
\end{preview}
  \caption{Difference in initial learning rate in wild-type models, without and with gain-decrease pre-training.
  Learning, $L(t)$ is defined in \eqref{eq:learning}.
  Here, we show the maximum and minimum values of this quantity when scanning all 6 relevant parameters (see \protect\hyperlink{par:pooled_scan}{text}).
  We see that this quantity is always negative, whereas it was positive in the experiments.
  }\label{fig:pooled_scan}
\end{figure}

@@

    \cline{1-8}
    Serial       & 10 & $0.12$  & $0.14$        & 0.5   & 0.89 & 0.9879 & 100 \\
    Two-state    & 2  & $0.1$   & $0.4$         & 0.5   & 0.7  & 0.91   & 5   \\
    Multistate   & 10 & $0.3$   & $0.3$         & 0.5   & 0.8  & 0.96   & 5   \\
    Pooled res.\ & 7  & $0.08$  & $[0.006,0.6]$ & 0.5   & 0.9  & 0.99   & 20  \\
    Cascade      & 14 & $0.386$ & $0.398$       & 0.478 & 0.63 & 0.99   & 200  \\
    Non-uni.\    & 12 & $0.4$   & $0.4$         & 0.5   & 0.7  & 0.99   & 500  \\
    \cline{1-8}
  \end{tabular}}
  \end{myenumA}
\end{preview}
  \caption[Simulation results for various models]{(\ref{fig:serial_ChR2}-\ref{fig:nonuni_ChR2}) Simulation results for various models, showing decrease in mean synaptic weight over time during gain increase training from the normal state (black) and after non-specific CF stimulation (cyan) for wild-type models.
  (\ref{tab:params_ChR2}) Parameters used for simulations.
  For the serial, two state and multistate models, the plasticity parameter listed is the transition probability between adjacent states.
  For the pooled resource model, the plasticity parameters are the minimum and maximum transition probability for the constituent two-state synapses.
  For the cascade and non-uniform multistate models, the plasticity parameter is the ratio of adjacent transition probabilities.}\label{fig:sim_ChR2}
\end{figure}
